Quantity discrimination, decision-making, and the role of early-life conditions in a lizard

### 2025-09-11 ms.qmd
updates

@@

@@

>>>>

```{r, sex_ratios}
#| label: sex_ratios
# Get the sex ratios for each treatment
sex <- c("m", "f")
trt <- c("A_23", "B_23", "A_28", "B_28")
for(s in sex){
  for(t in trt){
    count <- data_num %>%
      filter(day == 1, trt == t, sex == s) %>%
      nrow()

    name <- paste0(t, "_", s)   # e.g. "A_23_f"
    assign(name, count)
  }
}
```

@@

We recorded and analysed a total of 400 videos from 80 lizards (n = 20 per treatment, see @fig_results). The lizards were between `r min(data_num$age_raw)` and `r max(data_num$age_raw)` days post-hatching (see Fig. S5 in _Supplementary Material_). Final sample sizes were composed by 43 females and 37 males, with no less than 6 females per treatment and no more than 13.

@@

#### Lizards age by Treatment

```{r, fig-age_treatment}
#| label: fig-age
#| fig.cap: "Distribution of the age of the lizards by treatment"
# Plotting the distribution of the age of the lizards by treatment
#
plot_age_df <- data_num %>%
  mutate(trt = factor(trt, 
          levels = c("A_23", "B_23", "A_28", "B_28"), 
          labels = c("Cold-Control", "Cold-CORT", "Hot-Control", "Hot-CORT")))
#
plot_age <- ggplot(plot_age_df, aes(x = age_raw, color = trt)) +
  geom_density(aes(y = after_stat(count)), linewidth = 1.5) +
  scale_color_manual(values = c("Cold-CORT" = "#00008B",
                              "Cold-Control" = "#68bde1",
                              "Hot-CORT" = "#b50101",
                              "Hot-Control" = "#fa927d")) +  
  labs(y = "Number of lizards", x = "Age (days)", color = "Treatments") +
  theme_classic() +
  theme(plot.margin = margin(5.5, 5.5, 5.5, 5.5, "mm"),
    axis.text.y = element_text(size = 12, family = "Times"),   # Remove y-axis labels
    axis.title = element_text(size = 12, family = "Times"),
    axis.text = element_text(size = 10, family = "Times"),
    legend.position = "right",
    legend.title = element_text(size = 12, family = "Times"),
    legend.text = element_text(size = 11, family = "Times")
    ) 
#
ggsave("./output/figures/plot_age.png", plot=plot_age, width = 25, height = 18, units = "cm", dpi = 600)
knitr::include_graphics("./output/figures/plot_age.png")
```

Fig. S5 - Distribution of the age of the lizards by treatment
